---
title: "Class Excercise 1"
author: "Miguel, Patrick Stöckli, Tobias Hoesli"
date: "`r Sys.Date()`"
output:
  pdf_document:
    extra_dependencies: "subfig"
urlcolor: 'blue'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction

For this excersise we will be using the dataset **Quality of Governnment** Dataset.
Data from 1946 to 2021 with a country-year unit of analysis are available in a Basic Time Series (TS) dataset provided by the Quality of Government (QoG) Institute at the University of Gothenburg. The dataset contains both historical and contemporary versions of various nations. Data for nations prior to their independence is excluded, and factors with sparse coverage are eliminated. Basic descriptive numbers and a bar graph showing the availability of data for each year are provided in the codebook.
You can find the codebook [here](https://github.com/UniLuFS2020-ReplicationSeminar/Data_Mining_EX1/blob/f8314e3e5aef74dd7a3f3a26b7e0ffe7b2a4d3c3/data/codebook_bas_jan22.pdf).


### Research Questions

Based on the dataset we wanted to compose the following research questions:

1. Is there a relationship between the level of democracy and the share of women in lower and single houses of parliament?
2. How does the percentage of adherents to Islam in a country affect the share of women in lower and single houses of parliament?
3. Does real GDP per capita have an impact on the share of women in lower and single houses of parliament?


### Empirical Hypotheses

Higher degrees of democracy may lead to more open political structures and, as a result, a higher proportion of women in lower and single houses of parliament. We hypothesize that greater levels of democracy will result in a higher proportion of women serving in the lower and single houses of parliament.
  
The proportion of women in the lower and single houses of parliament may be lower in nations with greater percentages of Muslims due to cultural or religious norms that restrict women's involvement in politics. We therefore hypothesize that there will be fewer women in lower and single houses of parliament in nations with greater rates of Islamic adherents.




## Methods 


### Visualizations

Data Exploration

### Regressionanalyisis




```{r Load TS Data and Regressions, warning=FALSE, message=FALSE}

source("../code/regression.R")

```


```{r Regression side by side, echo=FALSE, warning=FALSE, message= FALSE, fig.show="hold", out.width="50%"}
par(mar = c(4, 4, .1, .1))
#Level of Democracy 
ggplot(data_ts_2, aes(x = fh_ipolity2, y = ipu_l_sw)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Level of Democracy (Freedom House/Imputed Polity)", y = "Share of Women (Lower and Single Houses)")+
  ggtitle("Regression Analysis by Level of Democracy")


#Islam: Total (%Adherents)
ggplot(data_ts_2, aes(x = arda_isgenpct, y = ipu_l_sw)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Islam: Total (% Adherents)s", y = "Share of Women (Lower and Single Houses)")+
  ggtitle("Regression Analysis by % of adherents to Islam")

```

```{r Part 2 Regressions, echo=FALSE,warning=FALSE, message= FALSE, fig.show="hold", out.width="50%"}
par(mar = c(4, 4, .1, .1))
#Real GDP per Capita
ggplot(data_ts_2, aes(x = mad_gdppc, y = ipu_l_sw)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "GDP per Capita", y = "Share of Women (Lower and Single Houses)")+
  ggtitle("Regression Analysis by GPD per Capita")
# All independent variables 
ggplot(data_ts_2, aes(x = arda_isgenpct+fh_ipolity2+mad_gdppc, y = ipu_l_sw)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Independent Variables", y = "Share of Women (Lower and Single Houses)")+
  ggtitle("Regression Analysis by All Independent Variables")



```
  

```{r Stargazer Regressionanalysis, results='asis'}
#Load package "labelled" to generate table
library(stargazer)

#Generate a well-formatted table
stargazer(regression_a, regression_b, regression_c, 
          title="Regression on the Share of Women in Parliament (Lower and Single Houses) ", 
          dep.var.caption="", 
          dep.var.labels.include=FALSE,
          covariate.labels=c("Islam","Level of Democracy", "Real GDP per Capita"), 
          digits=2,
          keep.stat=c("rsq", "adj.rsq", "n"), 
          notes=c("Notes: Standard errors in parentheses."), 
          notes.align = "c", 
          notes.label="",
          no.space=TRUE,
          type = 'latex')
```

\newpage

## Results  

In the graphics aswell as in the regression we see that having Islam as State religion it has a negative influence on the womens' share in parliament and the democracy index.
In the regression we controlled for additional variables. Even though the data is one sided we would need to consider more variables that could have on womens' share and democracy index next to Islam. With this data alone we cannot conclude that Islam is the only nor the biggest factor that has influence on the above mentioned points.
